### 2024-07-03 causal-inference.qmd
20240702 - spelling

It is important not to control for the collider (fan attendance).
If you control for the collider, you can induce an artificial association between team record and coaching quality.
Moreover, because doing so induces an artificial association between team record and coaching quality, it can also induce an artifial association between the effects of team record and coaching quality: number of media articles about the team and fantasy points, respectively.
That is, controlling for the collider can lead to an artificial association between `X` and `Y` that does not reflect a causal process.

>>>>

It is important not to control for the collider (fan attendance).
If you control for the collider, you can induce an artificial association between team record and coaching quality.
Moreover, because doing so induces an artificial association between team record and coaching quality, it can also induce an artificial association between the effects of team record and coaching quality: number of media articles about the team and fantasy points, respectively.
That is, controlling for the collider can lead to an artificial association between `X` and `Y` that does not reflect a causal process.
